---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 120)
```
# wactor

<!-- badges: start -->
<!-- badges: end -->

A user-friendly factor-like interface for converting strings of text into numeric vectors and rectangular data structures.

## Installation

<!-- You can install the released version of wactor from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wactor")
```
-->

You can install the development version from [GitHub](https://github.com/mkearney/wactor) with:

``` r
## install {remotes} if not already
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}
## install wactor for github
remotes::install_github("mkearney/wactor")
```
## Example

Here's some basic text (e.g., natural language) data:

```{r example}
## load wactor package
library(wactor)

## text data (sentences)
s1 <- c(
  "This test is a test",
  "This one will be a test",
  "This this was a test"
)
s2 <- c(
  "This test is going to be a test",
  "This one will have been a test",
  "This this has been a test"
)
```

Use `wactor()` to convert a character vector into numeric vectors/matrix:

```{r}
## create wactor
w <- wactor(s1)
```

Get the document term frequency matrix

```{r}
## term frequency–inverse document frequency
dtm(w)

## same thing as dtm
predict(w)
```

or term frequency–inverse document frequency matrix

```{r}
## apply to other data
tfidf(w)
```

Or apply the wactor on **new data**

```{r}
## document term frequecy of new data
dtm(w, s2)

## same thing as dtm
predict(w, s2)

## term frequency–inverse document frequency of new data
tfidf(w, s2)
```

